### 2021-12-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@2308ff5b6b0725a98a3dfe4d0d5fd9f0f24228b9 🚀

\[
\frac{tp\times tn - fn\times fp}{\srt{(tp+fp)\times (tp+fn)\times (tn+fp)\times (tn+fn)}} \,.
\]

@@

The results presented here highlight an interesting paradox: although
the Random Forest was ultimately able to get a correct estimate of
network structure tbl.~\ref{tbl:comaprison}, it ultimately remains a
poor classifier, as evidenced by its low PR-AUC. This suggests that the
goal of predicting \emph{interactions} and predicting \emph{networks}
may not be solvable in the same way -- of course a perfect classifier of
interactions would make a perfect network prediction; but even the best
scoring predictor of interactions (the ensemble model) had not
necessarilly the best prediction of network structure. The tasks of
predicting networks structure and of predicting interactions within
networks are essentially two different ones. For some applications
(\emph{.e.g.} comparison of network structure across gradients), one may
care more about a robust estimate of the structure, at the cost at
putting some interactions at the wrong place. For other applications
(\emph{e.g.} identifying pairs of interacting species), one may
conversely care more about getting as many pairs right, even though the
mistakes accumulate in the form of a slightly worse estimate of network
structure. How these two approaches can be reconciled is undoubtedly a
task for further research. Despite this apprent tension at the heart of
the predictive exercise, we can use the results presented here to
suggest a number of guidelines.

>>>>

\[
\frac{tp\times tn - fn\times fp}{\sqrt{(tp+fp)\times (tp+fn)\times (tn+fp)\times (tn+fn)}} \,.
\]

@@

The results presented here highlight an interesting paradox: although
the Random Forest was ultimately able to get a correct estimate of
network structure tbl.~\ref{tbl:comparison}, it ultimately remains a
poor classifier, as evidenced by its low PR-AUC. This suggests that the
goal of predicting \emph{interactions} and predicting \emph{networks}
may not be solvable in the same way -- of course a perfect classifier of
interactions would make a perfect network prediction; but even the best
scoring predictor of interactions (the ensemble model) had not
necessarilly the best prediction of network structure. The tasks of
predicting networks structure and of predicting interactions within
networks are essentially two different ones. For some applications
(\emph{.e.g.} comparison of network structure across gradients), one may
care more about a robust estimate of the structure, at the cost at
putting some interactions at the wrong place. For other applications
(\emph{e.g.} identifying pairs of interacting species), one may
conversely care more about getting as many pairs right, even though the
mistakes accumulate in the form of a slightly worse estimate of network
structure. How these two approaches can be reconciled is undoubtedly a
task for further research. Despite this apprent tension at the heart of
the predictive exercise, we can use the results presented here to
suggest a number of guidelines.
